---
title: "Simulation"
output: html_notebook
---

Preperation

```{r}
library(stats)
library(PearsonDS)
library(dplyr)
library(magicfor)
library(gsl)
```
Design
```{r}
sample1 <- c(15,20,65,100)
sample2 <- c(20,25,100,145)
#effect size
es <- c(0, 0.2,0.5,0.8)
#variance
var1 <- c(3)
var2 <- c(3,9)
#distribution
distr <- c("normal", "positive skew", "negative skew")
#matrix(full factorial)
Design <- expand.grid(sample1=sample1, sample2=sample2, es=es, var1=var1, var2=var2, distr=distr)

```
Data Generation
```{r}
MyDataGeneration <- function(sample1, sample2, es, var1, var2, distr){
  if(distr=="normal"){
    moments1 <- c(mean=0, variance=var1, skewness=0, kurtosis=3.0)
    moments2 <- c(mean=0+(es*(sqrt(((sample1-1) *(var1)+(sample2-1)*(var2))/(sample1+sample2-2)))), variance=var2, skewness=0, kurtosis=3.0)
  } 
   if(distr=="positive skew") {
    moments1 <- c(mean=0, variance=var1, skewness=0.5, kurtosis=5.0)
    moments2 <- c(mean=0+(es*(sqrt(((sample1-1) *(var1)+(sample2-1)*(var2))/(sample1+sample2-2)))), variance=var2, skewness=0.5, kurtosis=5.0)
  }
  if(distr=="negative skew") {
    moments1 <- c(mean=0, variance=var1, skewness=-0.5, kurtosis=5.0)
    moments2 <- c(mean=0+(es*(sqrt(((sample1-1) *(var1)+(sample2-1)*(var2))/(sample1+sample2-2)))), variance=var2, skewness=-0.5, kurtosis=5.0)
  }
  gen1 <- rpearson(n=sample1, moments=moments1)
  gen2 <- rpearson(n=sample2, moments=moments2)
  Y <- c(gen1, gen2)
  group <- as.factor(c(rep(1, times=length(gen1)), rep(2, times=length(gen2))))
  SimData <- data.frame(Y,group)
  return(SimData)
}


```
Old Test
```{r}
#Welch´s T-test
Method_old<- function(SimData){
  formula <- Y~group
  res <- t.test(formula, data = SimData)
  return <- res
}
```

Trimmed sample
```{r}
trim.sample <- function(s){
  s.test <- s
  s_minus_med <- s.test-median(s)
  K <- 2.24 #multiplier of the median absolute deviation
  index <- ((s_minus_med < (-K*mad(s))) | (s_minus_med > K*mad(s))) #identifies elements 
  t <- s_minus_med[index]
  t_plus_med <- t + median(s)
  s_trim <- s.test[!s.test %in% t_plus_med]
  return(s_trim)
}
```

Trimming Proportions(g1,g2)
```{r}
#returns trimming proportion g1 (number of observations)
trim.proportion.left <- function(s){
  s.test <- s
  s_minus_med <- s.test-median(s)
  K <- 2.24 #multiplier of the median absolute deviation
  index <- ((s_minus_med < (-K*mad(s)))) #identifies elements 
  t <- s_minus_med[index]
  return(length(t))
}
#returns g2
trim.proportion.right <- function(s){
  s.test <- s
  s_minus_med <- s.test-median(s)
  K <- 2.24 #multiplier of the median absolute deviation
  index <- ((s_minus_med > K*mad(s))) #identifies elements 
  t <- s_minus_med[index]
  return(length(t))
}
```
Winzorised sum of squared deviations for one sample
```{r} 
#update 23.04.2020
SSDwin <- function(x){
  #x= sample of any size
  x.test <- sort(x)
  n <- length(x.test)
  x_trim <- sort(trim.sample(x.test))
  g1 <- trim.proportion.left(x.test)
  g2 <- trim.proportion.right(x.test)
  max_x_trim <- max(x_trim)
  hx <- length(x.test)-g1-g2
  trim_mean_x <- sum(x_trim)/hx
  step1 <- (g1+1)*((x_trim[1]-trim_mean_x)^2)
  step2 <- sum((x_trim[2:length(x_trim)-1]-trim_mean_x)^2)
  step3 <- ((g2+1)*(x_trim[max_x_trim]-trim_mean_x)^2)
  step4 <- ((g1*(x_trim[1]-trim_mean_x))+(g2*(x_trim[max_x_trim]-trim_mean_x)))^2
  ssd <- (step1+step2+step3+step4)/n
  return(ssd)
}

```


My New Test (Trimmed F-Test with winsorizd SSD)
```{r}
MyMethod_new <- function(SimData){
  group1 <- filter(SimData, group==1)
  group2 <- filter(SimData, group==2)
  x<- sort(group1[,1])
  y <- sort(group2[,1])
  J <- 2 #number of groups
  x_trim<- sort(trim.sample(x)) #sample after trimming
  y_trim <- sort(trim.sample(y)) #sample after trimming
  g1x <- trim.proportion.left(x)
  g1y <- trim.proportion.left(y)
  g2x <- trim.proportion.right(x)
  g2y <- trim.proportion.right(y)
  hx <- length(x) - g1x - g2x#sample size after trimming
  hy <- length(y) -g1y - g2y
  H <- sum(hx,hy)
  trim_mean_x <- sum(x_trim)/hx
  trim_mean_y <- sum(y_trim)/hy
  mean_population <- ((hx*trim_mean_x)/H) + ((hy*trim_mean_y)/H)
  nominator_x <- ((trim_mean_x - mean_population)^2) / (J-1)
  nominator_y <- ((trim_mean_y - mean_population)^2) / (J-1)
  nominator <- nominator_x + nominator_y
  SSDx <- SSDwin(x=x)
  SSDy <- SSDwin(x=y)
  SSD_x_y <- sum(SSDx,SSDy)
  denominator <- SSD_x_y/(H-J)
  f <- as.matrix(nominator/denominator)
  p_val_bigger <- pf(q=f, df1=(J-1), df2=(H-J), lower.tail=TRUE)
  p_val_smaller <- pf(q=f, df1=(J-1), df2=(H-J),lower.tail=FALSE)
  p_val_twosided <- 2*min(p_val_bigger,p_val_smaller)
  p.value <- as.matrix(p_val_twosided)
  results<- rbind(f,p.value)
  return(results)
}
```


My Simulation
```{r}
MySimulationCell<- function(Design = Design, RowOfDesign = 1, K = 2){
  # Input arguments:
  #Design = designmatrix
  # RowOfDesign: number that refers to the row of the design matrix = one cell
  # K: Total number of replications = number of data sets generated in one cell
  #Create matrix or dataframe to store the results:
  MyResult <- matrix(NA, nrow = K, ncol=2)
  # Analyze data set with Method_new
  tmp <- proc.time()
  #create a loop over the replications k = 1 to K:
  for (k in 1:K){
    # Generate data
    # set a random number seed to be able to replicate the result exactly
    set.seed((k + 1000)*RowOfDesign)
    SimDat <- do.call(MyDataGeneration, Design[RowOfDesign,] )
    MyAnalysisResult1 <- MyMethod_new(SimDat)
    #Analyze data set with Method_old
    MyAnalysisResult2 <- Method_old(SimDat)
    #Combine relevant results of the analysis by the two methods in a vector (optional)
    MyAnalysisResult <- c(MyAnalysisResult1[2,], MyAnalysisResult2$p.value)
    #Evaluate the analysis results of Method_new (Result1) and Mehtod_old (Result2)
    P_old <- MyAnalysisResult2$p.value
    P_new <- MyAnalysisResult1[2,]
    #Evaluation
    reject_old <- 0
    reject_new <- 0
      #Type I error
      if(P_old < 0.05){
        reject_old <- reject_old + 1
      }
    tryCatch({
      if(P_new < 0.05){
        reject_new <- reject_new + 1
      }},
        error=function(cond) {
           browser()
        }
      )
    #store the results in the right row k of your result matrix:
    #We only store the second result which is the evaluation criterion
    MyResult[k, ] <- c(reject_old,reject_new)
  }
  #save the time to run the analyses of K data sets in one cell of the design.
  time <- proc.time() - tmp
  attr(MyResult,'time')<-time
  return(MyResult)
}

```
For one Row, can be used as test run
```{r}
Row <- 1
MyResult <- MySimulationCell(Design = Design, RowOfDesign = Row, K = 10 )
```
For all Rows
```{r}
TotalCells <- nrow(Design)
magic_for(put, silent = T)
for (i in 1:TotalCells){
  Row <- i
  MyResult <- MySimulationCell(Design = Design, RowOfDesign = Row, K = 5000)
 put(MyResult)
}
MyResult <- magic_result()
```
Significance check for errors of Welch´s t-test and F-test with McNemar test. Result: Pvalue and, if significant, Sig= true
```{r}
#Nemar test which takes the calculated result per test from MyResult as inputs
pVal <- function(Method1,Method2){
  return(mcnemar.test(factor(Method1,levels=c(0,1)),factor(Method2,levels=c(0,1)))$p.value)
}
#keep in mind that 382 is the number of rows in design
magic_for(put, silent=T)
for(i in 1:TotalCells){
Methods <- MyResult[["MyResult"]][[i]]
Method1 <- Methods[,1]
Method2 <- Methods[,2]
pvalue <- pVal(Method1, Method2)
put(pvalue)}
pvalue <- magic_result_as_vector()
pvalue[is.na(pvalue)] <- 9
pvalue <- round(pvalue, digits=3)
sig <- c(TRUE, FALSE)
magic_for(put, silent=T)
for(i in 1: length(pvalue)){
  if(pvalue[i] < 0.05){
    sig <- TRUE
  }else{
    sig <- FALSE
  }
  put(sig)
}
sig <- magic_result_as_vector()


```


My Evaluation, Calculation of Type I error and Power rates
```{r}
#Welch´s T-test
magic_for(put, silent = T)
for(i in 1:TotalCells){
  ResultRow <- MyResult[["MyResult"]][[i]]
  Column<- ResultRow[,1]
  Amount_Error <- Column[Column==1]
  Amount_Error <- length(Amount_Error)
  Rate <- Amount_Error/(length(Column))
  put(Rate)
}
number_reject_old <- magic_result_as_vector() #this is type I error rate for es = 0 and power for es != 0

#Trimmed T Test
magic_for(put, silent = T)
for(i in 1:TotalCells){
  ResultRow <- MyResult[["MyResult"]][[i]]
  Column<- ResultRow[,2]
  Amount_Error <- Column[Column==1]
  Amount_Error <- length(Amount_Error)
  Rate <- Amount_Error/(length(Column))
  put(Rate)
}
number_reject_new <- magic_result_as_vector() #this is type I error rate for es = 0 and power for es != 0

dif <- c(number_reject_old - number_reject_new)
RateResults <- data.frame(number_reject_old,number_reject_new)
fullRes <- cbind(Design, RateResults, pvalue,sig,dif)
```


```{r}
save("fullRes", file="ResultsFullDesignRep5000.Rdata")
```



